---
title: "classification_tree"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(tree)
library(caret)
library(randomForest)
library(gbm)
library(ROCR)
library(MLmetrics)
data = read.csv("online_shoppers_intention.csv")
data$Weekend = as.factor(data$Weekend)
data$OperatingSystems = as.factor(data$OperatingSystems)
data$Browser = as.factor(data$Browser)
data$TrafficType = as.factor(data$TrafficType)
data$VisitorType = as.factor(data$VisitorType)
```

```{r}
#set.seed(928)
train = sample(1:nrow(data), nrow(data)*7/8)
data.test = data[-train,]
data.train = data[train,]
rev.train = data$Revenue[train]
rev.test = data$Revenue[-train]
```

```{r}
tree.data = tree(Revenue~., data.train)
plot(tree.data)
text(tree.data, pretty = 0)
tree.pred = predict(tree.data,data.test)
pred.factor = ifelse(tree.pred >= 0.1, TRUE,FALSE)
```

```{r}
confusionMatrix(table(rev.test,pred.factor), positive = 'TRUE')
```

The idea:
People fall into 3 categories: unlikely to buy at all, possibly likely, and very likely. We want to identify and target those who are possibly likely to buy something, with the goal of influencing them to finish the transaction.

Using cross-validation to confirm that splitting past pageValues is only marginally helpful.
```{r}
#cv.tree = cv.tree(tree.data)
#plot(cv.tree$size, cv.tree$dev, type = "b")
```

## Bagging

```{r}
bag.tree = randomForest(Revenue~., data = data.train, mtry = 17, importance = TRUE, ntrees = 500, replace = TRUE)
bag.pred = predict(bag.tree, data.test)
```

```{r}
bag.pred.factor = ifelse(bag.pred >= 0.2, TRUE,FALSE)
confusionMatrix(table(bag.pred.factor,rev.test), positive = 'TRUE')
varImpPlot(bag.tree)
#bag.tree

prcurve = prediction(bag.pred,rev.test)
prcurve = performance(prcurve, "prec","rec")
#plot(prcurve)

PRAUC(bag.pred,rev.test)

```

"Considering that the “Page Value” [12] feature represents the page
that a user visited before completing an e-commerce transaction, it can be seen as a
natural measure of visitor’s transaction finalization intention. In our system, this feature
is represented as the average of the "Page Value" values of pages visited by the visitor
during the session and is updated when the visitor moves to another page."

## Boosting
```{r}
#set.seed(1337)
numtrees = c(1000,1500,2000,3000)
shrink = c(.1,.02,.01,.005,.008)
best_n = 0
best_s = 0
best_auc = 0
best_prcurve = NaN

for (n in numtrees) {
  for (s in shrink) {
    boost.data = gbm(Revenue~., data = data.train[-c(3,4,10,11,12,13,14,15,16,17)],n.trees = n, shrinkage = s, distribution = "bernoulli")
    boost.pred = predict(boost.data, newdata = data.test, n.trees = n)
    predictions = exp(boost.pred)/(1 + exp(boost.pred))
    pred.factor = ifelse(predictions >= 0.2, TRUE,FALSE)

    #confusionMatrix(table(rev.test,pred.factor), positive = "TRUE")
    prcurve = prediction(boost.pred,rev.test)
    prcurve = performance(prcurve, "prec","rec")
    #plot(prcurve)

    auc = PRAUC(boost.pred,rev.test)
    if (auc > best_auc) {
      best_auc = auc
      best_n = n
      best_s = s
      best_prcurve = prcurve
    }
  }
}

best_auc
best_n
best_s
#summary(boost.data)
```
Show plot for best auc
```{r}
plot(best_prcurve)
```


```{r}
boost.data = gbm(Revenue~., data = data.train,n.trees = 1000, shrinkage = 0.01, distribution = "bernoulli")
boost.pred = predict(boost.data, newdata = data.test, n.trees = 1000)
predictions = exp(boost.pred)/(1 + exp(boost.pred))
pred.factor = ifelse(predictions >= 0.5, TRUE,FALSE)

confusionMatrix(table(rev.test,pred.factor), positive = "TRUE")

prcurve = prediction(boost.pred,rev.test)
prcurve = performance(prcurve, "prec","rec")
plot(prcurve)

PRAUC(boost.pred,rev.test)
```